False Positive Probabilities for all Kepler Objects of Interest: \\ \nvalnew\ newly validated planets and \nfpnew\ likely false positives

### 2015-07-29 ms.tex
more stellar parameter discussion re: D13

\defcitealias{Morton:2012}{M12}
\defcitealias{Huber:2014}{H14}

@@

\autoref{fig:starsteff} and \autoref{fig:starsfehradius} compare the
estimated effective temperatures, metallicities, and radii, derived
here to those independently determined for the official
\kepler\ stellar properties catalog \citep[][hereafter
  \citetalias{Huber:2014}]{Huber:2014}.  While there is largely
general agreement, there are also discrepancies, highlighting the
difficulty of estimating physical stellar properties.  In particular,
we note that for stars which \citetalias{Huber:2014} list as $T_{\rm eff}
< 4000$\,K, \isochrones\ predicts systematically hotter temperatures.
Most of the \citetalias{Huber:2014} properties for these stars are
taken from \citet{dressing:2013}.

>>>>

\defcitealias{Morton:2012}{M12}
\defcitealias{Huber:2014}{H14}
\defcitealias{Dressing:2013}{D13}

@@

\autoref{fig:starsteff} and \autoref{fig:starsfehradius} compare the
estimated effective temperatures, metallicities, and radii, derived
here to those independently determined for the official
\kepler\ stellar properties catalog \citep[][hereafter
  \citetalias{Huber:2014}]{Huber:2014}.  While there is largely
general agreement, there are also discrepancies, highlighting the
difficulty of estimating physical stellar properties.

In particular, we note that for stars which \citetalias{Huber:2014}
list as $T_{\rm eff} < 4000$\,K, \isochrones\ predicts systematically
hotter temperatures.  Most of the \citetalias{Huber:2014} properties
for these stars are taken from
\citet[][\citetalias{dressing:2013}]{dressing:2013}.  Those properties
were determined by trying to match the colors of each star to the colors
of a grid of model stars from the Dartmouth models, supplemented by
some interpolation.  \citetalias{dressing:2013} also imposed priors
on [Fe/H] and the height of stars above the plane of the Galaxy.  To
validate their methodology, \citetalias{dressing:2013} compare their
predictions of 26 nearby stars (with parallax)
